---
title: "Report template title"
author: "Ben Fasoli"
output: github_document
---

Revised: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, fig.width = 9)
```


#### Text formatting

We can include markdown formatting for **bold**, *italic*, ***both***, [links](https://air.utah.edu), `code` and LaTex formatting for inline equations (such as styling subscripts for $\text{CO}_2$).


#### Tables

We can create tables using hyphens `-` and pipes `\` such as

Short         | Long
------------- | --------------------
$\text{CO}_2$ | Carbon Dioxide
$\text{CH}_4$ | Methane


#### Lists

Lists can be ordered automatically using numbers

1. One
1. Two
1. Three

or bulleted

- One
- Two

and can have sub points with two spaces before the dash

- One
  - a
  - b


#### Code

R code can be included inline using `r print('Hi')` or in longer blocks such as

```{r}
plot(1:10)
```

For code that we want rendered but not run (such as to syntax highlight another language), we omit the {} and specify the language such as

```css
h1 {
  color: #000;
}
```